---
title: "CGN Data"
author: "Denver Ncube"
date: "6/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(car)
library(reshape2)
library(data.table)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(plotly)
library(pastecs)
library(gridExtra)
library(readxl)
```

```{r}
CG <- read.table('~/Desktop/ADVANCED BIOSTATS/FOR R.csv', sep = ",",header =T)
CG
#group_by(DF)%>%summarise(avg= mean(Total.GFP))
```
# this part is not required: 


```{r}


```
#Next split the data sets into 3 parts to then strictly analyze the trends
```{r}
#Plot for GFP.CGN
CGN <- ggplot(CG) +
  aes(x = Region, y= Percentage, fill= Region) + 
  geom_boxplot() + 
 # geom_violin()+
  scale_fill_manual(values=c("green", "magenta", "blue")) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 110))+
  geom_jitter()+
  ggtitle("Cholinergic and GABAergic vTely321 neurons") + theme(plot.title =  element_text(size=12))+ 
  xlab("Forebrain Region") + ylab("Percentage %") +
  theme_classic()
CGN
#Now to constrain the width, arrange the 
 A <- grid.arrange(CGN, ncol= 3)
 A
#ggsave("Fig_5.png", Fig_5)
#Fig_2 <- grid.arrange(CGN, NCGN, nrow=1)
#ggsave("Fig_2.jpeg", Fig_2)
```

```{r}


CG$Region <- factor(CG$Region,
    levels = c('RT','MT', 'CT'),ordered = TRUE)
factor(CG$Region,levels = rev(levels(CG$Region)),ordered = TRUE)

GGA <- ggplot(CG) +
    aes(x = Region, y= Vp, fill= Region) +
  geom_boxplot() + #geom_violin()+ 
  scale_fill_manual(values=c("green", "magenta", "blue")) +
  geom_jitter()+
 scale_y_continuous(expand = c(0, 0), limits = c(0, 100))+
  ggtitle("CGNeurons at 48hpf") + theme(plot.title = element_text(size=12)) +
 xlab("Forebrain region") + ylab("Percentage %") +
  theme_classic()
GGA

#Plot for GFP VACHTb 
VG <- ggplot(CG) +
  aes(x = Region, y= Gp, fill= Region) +
  geom_boxplot() + #geom_violin()+
  scale_fill_manual(values=c("green", "magenta", "blue")) +
  geom_jitter()+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100))+
  ggtitle("CGNeurons at 4dpf") + theme(plot.title = element_text(size=12))+
  xlab("Forebrain region") + ylab("Percentage %") +
  theme_classic()
VG

A <- grid.arrange(GGA, VG, ncol= 3)
 A
```





```{r}

CG$Region <- factor(CG$Region,
    levels = c('CT','MT', 'RT'),ordered = TRUE)
factor(CG$Region,levels = rev(levels(CG$Region)),ordered = TRUE)

CG$Region <- with(CG, relevel(Region, "RT"))
ggplot((CG)+ aes(x= Region)) + geom_boxplot() +
         scale_fill_manual(values=c("green", "magenta", "blue")) + 
         scale_y_continuous(expand = c(0, 0), limits = c(0, 110))+
         ggtitle("Cholinergic and GABAergic vTely321 neurons") + theme(plot.title = element_text(size=12))+  xlab("Forebrain Region") + ylab("Percentage %") +
  theme_classic()
#R <- factor(CG$Percentage),levels = rev(levels(CG$Percentage)), ordered = TRUE)
#R
```



#Pick out only the 
#C <- bind_rows(RT, MT, CT)
#C
#make historgrams by region 
#TOTAL  GFP 
#Plot for GFP.GABA
#GGA <- ggplot(DF) +
#  aes(x = REGION, y= BOTH, fill= REGION) +
#  geom_boxplot() + #geom_violin()+ 
#  scale_fill_manual(values=c("green", "magenta", "blue")) +
  #geom_jitter()+
#  scale_y_continuous(expand = c(0, 0), limits = c(0, 100))+
#  ggtitle("CGNeurons at 48hpf") + theme(plot.title = element_text(size=12))+
# xlab("Forebrain region") + ylab("Percentage %") +
#  theme_linedraw()
#GGA

#Plot for GFP VACHTb 
VG <- ggplot(DF) +
  aes(x = REGION, y= X.GFP.VACHTb, fill= REGION) +
  geom_boxplot() + #geom_violin()+
  scale_fill_manual(values=c("green", "magenta", "blue")) +
  #geom_jitter()+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100))+
  ggtitle("CGNeurons at 4dpf") + theme(plot.title = element_text(size=12))+
  xlab("Forebrain region") + ylab("Percentage %") +
  theme_linedraw()
VG






#Not needed 
#GFP <- ggplot(DF) + aes(x = REGION, y =Total.GFP, fill= REGION) + geom_boxplot() + scale_fill_manual(values=c("red2", "royal blue", "magenta")) + geom_jitter()+  facet_wrap(~REGION, scales="free_x")+ ggtitle("Total GFP positive Neurons by Region") + theme(plot.title = element_text(size=12))+ xlab(NULL) + ylab(NULL) + theme_bw()
#Plot for non-GFP cells but CGN
#NCGN <- ggplot(DF) + aes(x = REGION, y= BOTH, fill= REGION) + geom_boxplot() + scale_fill_manual(values=c("red2", "royal blue", "magenta")) + geom_jitter()+ facet_wrap(~REGION, scales="free_x")+ ggtitle("Dual non-GFP positive CGN ") + theme(plot.title = element_text(size=12))+ xlab(NULL) + ylab(NULL) + theme_bw()


```{r}
VX <- ggplot(DF) +
  aes(x = REGION, y = VACHTB, fill= REGION) +
  geom_boxplot() +
  scale_fill_manual(values=c("red2", "royal blue", "magenta")) +
  geom_jitter()+
  #geom_volcano(position = position_nudge(x=0.2, y=), adjust = 2)+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.3))+
  #facet_wrap(~REGION, scales="free_x")+
  ggtitle("Percentage of GFP positive cholinergic only Neurons by Region") + theme(plot.title = element_text(size=12))+
  xlab("Brain Region") + ylab("Percent") +
  theme_classic()
VX 

GX <- ggplot(DF) +
  aes(x = REGION, y =GABA, fill= REGION) +
  geom_boxplot() +
  scale_fill_manual(values=c("red2", "royal blue", "magenta")) +
  geom_jitter()+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.3))+
  #facet_wrap(~REGION, scales="free_x")+
  ggtitle("Percentage of GFP positive GABAergic only Neurons by Region") + theme(plot.title = element_text(size=12))+
  xlab("Brain Region") + ylab("Percent") +
  theme_classic()
GX

# Conclusion: Most of the cholinergic neurons are also GABAergic in the selected region. Caveat is that the sample was taken form 3 anatomical positions we would need to have thinner sections to come up with a volumetric measurement. 
##grid.arrange(VO, GO, nrow=1)
```

V_O <- ggplot(DF, aes(x = REGION, y = X.VACHTB, fill= REGION)) +
geom_point(show.legend = FALSE, alpha = 0.7) +
geom_dotplot() +
scale_color_viridis_d() +
scale_size(range = c(2, 12)) +
scale_x_discrete() + 
labs(x = 'Forebrain Region', y = 'Percentage of Cholinergic neurons') +
  theme_classic()
V_O

V2 <- ggplot(DF, aes(x = REGION, y = X.VACHTB, fill= REGION)) +
geom_point(show.legend = FALSE, alpha = 0.7) +
scale_color_viridis_d() +
scale_size(range = c(2, 12)) +
scale_y_log10() +
labs(x = 'Forebrain Region', y = 'Percentage of Cholinergic neurons')

ggplot(DF, aes(x = REGION, y = X.VACHTB, fill= REGION)) +
geom_point(show.legend = FALSE, alpha = 0.7) +
scale_color_viridis_d() +
scale_size(range = c(2, 12)) +
scale_x_discrete() +
labs(x = 'Forebrain Region', y = 'Number of Cholinergic neurons')

```{r}
L <- read.table('~/Desktop/ADVANCED BIOSTATS/LIMTF.csv', sep = ",",header =T)
L
```

```{r}
LIM <- ggplot(L) +
  aes(x = L[1:5,3], y = Average, fill= ) +
  geom_boxplot() + #geom_violin()+
  scale_fill_manual(values=c("green", "cyan", "red")) +
  #geom_jitter()+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100))+
  ggtitle("Average percentage of Vtel-y321 neurons expressing LIMTF") + theme(plot.title = element_text(size=12))+
  xlab("Forebrain region") + ylab("Percentage %") +
  theme_linedraw()
LIM
```

